HERMES : Hybrid ERror-corrector Model with inclusion of External Signals for nonstationary fashion time series

### 2021-12-22 hermes_paper/hermes_ieee.tex
Corrections - Section 4 - M4 + conclusion

We also assessed the performance of HERMES using the M4 weekly dataset \cite{makridakis2020m4}. The M4 dataset gathers 359 weekly time series and shows 3 main differences compare to our proposed fashion dataset. Firstly, sequences do not have the same length with sequence lengths lying between 93 and 2610 time steps. Secondly, as some of the sequences represent financial signals or some others are demographic sequences, the  359 time series show very distinct behaviours. Thirldy, compare to the fashion application, the time horizon of the prediction is set to 13 for the weekly dataset.

\textbf{Training}

\textcolor{blue}{reformuler}
The sequence are firstly resized in order to egalize their lenghts. For the shorter ones: the eval and the test set is removed (the last 26 steps). Then the remaining number of entire year is duplicated in order to egalize all the sequence at the longest one : 2610 time steps. As per time series parametric model training time depends on the sequence lenght, all time series are then croped. At the end, with the addition of the previously removed eval and test set, 300 time steps are kept for each sequence.

For this training, The horizon $h$ is set to 13 due to the M4 weekly test set size and the window size $w$ is fixed at 104. For the RNN part, the same architecture than describe in Figure~ \ref{fig:rnn_architecture} is used. The Adam optimizer is used with a learning rate fixed at 0.005 and a batch size set at 8. As the loss function, the same loss than the fashion application is used. As the M4 weekly dataset is small, a rolling window is used on the train set in order to increase the train number of example and improve the training. 5 windows are computed for each sequence for the RNN train set. An overview of our train, eval, test set split and the resizing of the shorter sequences is given in Figure~\ref{}.
The previous parameters: window size, learning rate, batch size and the number of train window per time series are set using a grid search.

\begin{figure*}
  \centering
    \includegraphics[width=1.\linewidth]{figure/M4_dataset}
  \caption{One of the shortest sequences of the M4 weekly dataset (93 time steps). In order to fit its predictor, the last complete year is duplicated in order to reach a total lenght of 300 time steps.}
\label{fig:m4dataset}
\end{figure*}

\textbf{Benchmarks}

The M4 competion provides a rich collection of benchmarks gatering statistical models and neural network approaches. The same candidates are used in this part as baseline. In addition, the hybrid model named \textit{Uber} of S.Smyl is added to provide an interesting comparison against the HERMES approach. For a complete description and references of the benchmarck models, see \cite{makridakis2020m4}. As a HERMES candidate, a version using TBATS is proposed and called \textit{hermes-tbats}. Following the M4 competition methodology, models are evaluated according to the MASE, the SMAPE and the OWA measure. A complete definition of these metrics is also proposed in \cite{makridakis2020m4}.

\textbf{Results and discussion}

The final results for the M4 weekly dataset are displayed in Table~\ref{tab:m4metricresults}. Considering the HERMES approach, \textit{hermes-tbats} outperforms all the benchmarcks. This results is partially induced by the use of TBATS per-time-series predictors which achieves striking results on the test set. Regarding the hybrid model proposed by S.Smyl, its accuracy remains low in comparison to \textit{tbats} and  \textit{hermes-tbats}. With this second application, two important conclusions can be done. Firstly, the striking results of \textit{hermes-tbats} confirm that the HERMES framework is a general framework, well suited for a large collection of forecasting tasks. Secondly, the accuracy gap between the 2 hybrid candidates validate the HERMES approach and illustrates the importance of a global framework able to leverage any kind of per-time-series predictors.

@@

\section{Conclusion}
\label{sec:conclusion}
The motivation of this paper was to present HERMES, a new hybird model for time series forecasting. This new framework is a really promising approach. By mixing the performance of local parametric models and a global neural network. The \textit{hermes-tbats} version clearly outperform traditional statistical methods and full neural network models. Furthermore, this new model is totally suited for dealing with external signals. With a fine pre-processing and a well-designed architecture, our hybrid framework succeed at leveraging our complex extra data and reach impressive accuracy level in term of classification. In addition to this article, a fashion dataset gathering a sample of $\numberts$ time series and a collection of weak signals is provided. We believe that this dataset hide really fine dynamics and interactions where complex models would express their potential. By making it publicly available, we hope that it will enhance the set of datasets for time series forecasting and pave the way for further explorations.
As a possible future work, a different inclusion of the weak signals can be design in the HERMES architecture. Focusing on the example with huge change of behaviors, a fine analysis of the predictive power of the collection of weak signals can be done. In the same way, an interesting improvment of the hybrid framework can be to introduce not a single but several neural networks trained at correcting different kinds of weaknesses and activate or not by a latent space. This latent space can be drive by the historical data or even more by the weak signals.

>>>>

We also assessed the performance of HERMES using the M4 weekly dataset \cite{makridakis2020m4}. The M4 dataset gathers 359 weekly time series and has 3 main differences compared to our proposed fashion dataset. Firstly, sequences do not have the same length with sequence lengths lying between 93 and 2610 time steps. Secondly, as some of the sequences represent financial signals or some others are demographic sequences, the  359 time series have very distinct scales and dynamics. Thirldy, compared to the previous fashion application, the time horizon of the prediction is set to 13 for the weekly dataset.

\textbf{Training. } The sequences are firstly resized in order to obatain a dataset with fixed time horizon. The eval and the test sets are removed for the shortest sequences (the last 26 steps). Then, the remaining number of entire year is duplicated in order to egalize all the sequence at the longest one : 2610 time steps \textcolor{red}{Pas sur de comprendre, reformuler}. As per time series parametric model training time depends on the sequence length, all time series are then croped. Finally, with the addition of the previously removed eval and test sets, 300 time steps are kept for each sequence \textcolor{red}{Pas sur de comprendre, reformuler}.

The horizon $h$ is set to 13 due to the M4 weekly test set size and the window size $w$ is set to 104. For the RNN part, the same architecture as the one described in Figure~ \ref{fig:rnn_architecture} is used. The Adam optimizer is used with a learning rate  equal to  0.005 and a batch size set to 8. As the M4 weekly dataset is small, a rolling window is used on the train set in order to increase the train number of examples and improve training results. Five windows are computed for each sequence for the RNN train set. An overview of our train, eval, test set split and the resizing of the shortest sequences is given in Figure~\ref{}.
The previous parameters: window size, learning rate, batch size and the number of train windows per time series are set using a grid search, see Appendix~\ref{}.

\begin{figure*}
  \centering
    \includegraphics[width=1.\linewidth]{figure/M4_dataset}
  \caption{One of the shortest sequences of the M4 weekly dataset (93 time steps). In order to fit its predictor, the last complete year is duplicated in order to reach a total length of 300 time steps.}
\label{fig:m4dataset}
\end{figure*}

\textbf{Benchmarks. } The M4 competion provides a rich collection of benchmarks gatering statistical models and neural network approaches. The same candidates are used in this part as baselines. In addition, the hybrid model named \textit{Uber} of S.Smyl is added. For a complete description and references of the benchmarck models, see \cite{makridakis2020m4}. As a HERMES candidate, a version using TBATS is proposed and called \textit{hermes-tbats}. Following the M4 competition methodology, models are evaluated according to the MASE, the SMAPE and the OWA measures. A complete definition of these metrics is proposed in \cite{makridakis2020m4}, see also Appendix~\ref{}.

\textbf{Results and discussion. } The final results for the M4 weekly dataset are displayed in Table~\ref{tab:m4metricresults}. Considering the HERMES approach, \textit{hermes-tbats} outperforms all the benchmarcks. This results is partially induced by the use of TBATS per-time-series predictors which achieves striking results on the test set. Regarding the hybrid model proposed by S.Smyl, its accuracy remains low in comparison to \textit{tbats} and  \textit{hermes-tbats}. With this second application, two important conclusions can be made. Firstly, the striking results of \textit{hermes-tbats} confirm that the HERMES framework is a general framework, well suited for a large collection of forecasting tasks. Secondly, the accuracy gap between the two hybrid candidates validates the HERMES approach and illustrates the importance of a global framework able to leverage any kind of per-time-series predictors.

@@

\section{Conclusion}
\label{sec:conclusion}
The motivation of this paper was to present HERMES, a new hybird model for time series forecasting. By mixing the performance of local parametric models and a global neural network, \textit{hermes-tbats} clearly outperforms traditional statistical methods and full neural network models on two forecasting tasks. Furthermore, this new model is totally suited to deal with external signals. With a fine pre-processing and a well-designed architecture, our hybrid framework succeeds at leveraging our complex extra data and reaches very promising accuracy levels in terms of classification. In addition to this article, a fashion dataset gathering a sample of $\numberts$ time series and a collection of weak signals is provided. We believe that this dataset contains really fine dynamics and interactions where complex models would express their potential. By making it publicly available, we hope that it will enhance the diversity of datasets for time series forecasting and pave the way for further explorations.
As a possible future work, designing new models for the weak signals would improve their inclusion  in the HERMES architecture. Focusing on the examples with huge changes of behaviors, a fine analysis of the impact of the collection of weak signals is the topic of ongoing works. In the same way, an interesting improvement of the hybrid framework can be to introduce not a single but several neural networks trained at correcting different kinds of weaknesses. An interesting perspective is to add a latent discrete label to select dynamically the regime shifts, i.e. which corrector model to use on-the-fly.
